---
title: Datasets in CSV format
---
---
```{r echo = FALSE, message = FALSE, warning = FALSE}
# run setup script
source(here::here("_common.R"))
library(aiuportal)
```

AIU provides CSV files for some of its data sets so as to make it possible to
automate download and processing by interested parties.

The file names adhere to the following convention:

> `<dataset group>_<YYYY>.csv`

The available data sets are:

* [ATC Pre-Departure Delays]{#atcpre-csv} (from 2016), `<dataset group>`=`atc_pre_departure_delays`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("atc_pre_departure_delays_\\d{4}.csv")
  ```
* [All Pre-Departure Delays]{#allpre-csv} (from 2020), `<dataset group>`=`all_pre_departure_delays`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("all_pre_departure_delays_\\d{4}.csv")
  ```
* [ATFM Slot Adherence]{#sltadh-csv} (from 2016), `<dataset group>`=`atfm_slot_adherence`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("atfm_slot_adherence_\\d{4}.csv")
  ```
* [CO2 Emission by State]{#co2-csv} (from 2010), `<dataset group>`=`co2_emmissions_by_state`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("co2_emmissions_by_state_\\d{4}.csv")
  ```
* [Horizontal Flight Efficiency]{#hfe-csv} (from 2015), `<dataset group>`=`horizontal_flight_efficiency`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("horizontal_flight_efficiency_\\d{4}.csv")
  ```
* [Vertical Flight Efficiency]{#vfe-csv} (from 2015), `<dataset group>`=`vertical_flight_efficiency`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("vertical_flight_efficiency_\\d{4}.csv")
  ```
* [Taxi-in Additional Time]{#txin-csv} (from 2018), `<dataset group>`=`taxi_in_additional_time`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("taxi_in_additional_time_\\d{4}.csv")
  ```
* [Taxi-out Additional Time]{#txout-csv} (from 2018), `<dataset group>`=`taxi_out_additional_time`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("taxi_out_additional_time_\\d{4}.csv")
  ```
* [ASMA Additional Time]{#asma-csv} (from 2018), `<dataset group>`=`asma_additional_time`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("asma_additional_time_\\d{4}.csv")
  ```
* [Airport Traffic]{#aptflt-csv} (from 2016), `<dataset group>`=`airport_traffic`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("airport_traffic_\\d{4}.csv")
  ```


## Legacy CSVs

AIU provides some data sets in CSV format (compressed using [bzip2][bzip2]).

**These files will be migrated to pure CSV files with a new file name similar to
the ones above.**

The file name convention we adopted is as follows:

> `<dataset group>_<YYYY>.csv.bz2`

where

> `<dataset group> = <dataset>_<group>`

For example `ert_dly_ansp_2012.csv.bz2` refers to en-rote delays data set with
ANSP breakdown for year 2012.


The datasets made available are:

* [Airport Arrival ATFM Delays]{#aptdly-csv} (from 2014): `<dataset group>`=`apt_dly`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("apt_dly_\\d{4}.csv")
  ```
* [Daily en-route delays]{#ertdly-csv}, `<dataset>`=`ert_dly`
  - [ANSP](/acronym/ansp/) group (see [list of ANSP's considered by PRU](../ansp)) (from 2008), `<group>`=`ansp`
    ```{r echo = FALSE, message = FALSE, warning = FALSE}
    gt_for_csvs("ert_dly_ansp_\\d{4}.csv")
    ```
  - Country FIR group (from 2013), `<group>`=`fir`
    ```{r echo = FALSE, message = FALSE, warning = FALSE}
    gt_for_csvs("ert_dly_ansp_\\d{4}.csv")
    ```
* Horizontal Flight Efficiency (from 2014), `<dataset group>`=`hfe`
  ```{r echo = FALSE, message = FALSE, warning = FALSE}
  gt_for_csvs("hfe_\\d{4}.csv")
  ```


[bzip2]: <https://en.wikipedia.org/wiki/Bzip2> "Wikipedia: bzip2"

