---
title: "Global benchmarking"
type: bibliography
---

EUROCONTROL PRU is engaged in a series of international comparison projects. 

*	United States / Europe - Since 2003, FAA and EUROCONTROL have jointly produced comparisons of operational performance using common data and agreed algorithms. As of 2013, the US/Europe comparison is performed under a Memorandum of Cooperation between the United States and the European Union. The series comprises reports for 2008, 2010, 2012, 2013, 2015, and 2017 (published April 2019). In light of COVID19, a more tailored comparison for the 2020 and 2021 is planned focussing on the regional response / impact of COVID19. The next regular (i.e. post-COVID) US/Europe comparison is foreseen for 2023.

*	A further benchmarking activity has been launched with Brazil (DECEA) and revolves around assessing the operational ANS performance at airports and en-route airspace capacity. Initially, a comparison report was published in the first half of 2021. Since then, DECEA and PRU have produced additional comparative performance reports. Both organizations participate in international working groups related to the operational benchmarking performance of the air navigation system (ANS) and the Global Air Navigation Plan (GANP).

::: {class="col-sm-6"}
:::: {class="container"}
::::: {class="row"}
:::::: {class="card-deck"}

```{r echo=FALSE}
blogdown::shortcode(
  "bootstrap-card-alt",
  img="flag_of_brazil.png",
  link="brazil/",
  title="Brazil",
  text="Our collaboration with Brazil.", 
  alt="Brazil", 
  command="Resize", 
  options="300x", 
  class="mb-2"
  )
```

```{r echo=FALSE, eval=FALSE}
blogdown::shortcode(
  "bootstrap-card-alt",
  img="flag_of_china.png",
  link="china/",
  title="China",
  text="Our collaboration with China.", 
  alt="China", 
  command="Resize", 
  options="300x", 
  class="mb-2"
  )
```

```{r echo=FALSE}
blogdown::shortcode(
  "bootstrap-card-alt",
  img="flag_of_usa.png",
  link="usa/",
  title="USA",
  text="Our collaboration with USA.", 
  alt="USA", 
  command="Resize", 
  options="300x200", 
  class="mb-2"
  )
```

::::::
:::::
::::
:::
